Automatic Singing Transcription

### 2023-12-02 report/paper.tex
updated to before training

\subsubsection{Jamendo Dataset}
This dataset one of the most popular datasets for AST and has been used by many state-of-the-art
AST models. It contains 20 English songs and 60 songs in other languages with word-aligned timestamped sequences \citep{JamendoLyrics}. This dataset
is a good candidate for training AST models because it is publicly available and it's popularity
makes it an excellent benchmark to compare against other models. However, it is still a relatively
small dataset and does not contain any phoneme sequences. The authors of this dataset were able to
achieve a 77.8\% Word Error Rate (WER) which still leaves a lot of room for improvement.
{
\color{red}
Remember to record the performance of the state of the art models on this dataset
}
% \subsubsection{Children's Songs Dataset} All Korean :(
\subsubsection{MUSDB18}
MUSEDB18 is a dataset of 150 songs with isolated vocals and accompaniment tracks \citep{musdb18}. This
dataset is a good candidate for training AST models because it is publicly available and it has
clean isolated vocals. The downside of this dataset is that it doesn't contain any word level
timestamps. However, with the CTC technique mentioned in \ref{sec:utteranceToPhoneme}, this dataset
can still be used to train AST models.

@@

{
\color{red}
TODO: Add more detail about HMMs
TODO: Write about Dynamic Time Warping
TODO: Write about some results of HMMs
}

@@

For the word alignment task, WhisperX uses an external phoneme alignment approach to generate
word level timestamps using phoneme level timestamps \citep{whisperX}. The external phoneme
alignment model was actually a wav2vec 2.0 model that used Dynamic Time Warping (DTW) to align
the phonemes \citep{whisperX}. The first and last phonemes of each word were used to generate
the word level timestamps \citep{whisperX}.

@@

\section{Method}
\begin{enumerate}
    \item Preprocess datasets
    \item Augment datasets
    \item Create frankenstein dataset
    \item Train model
    \item Evaluate model
    \item Label unlabeled datasets
    \item train student model on newly labeled datasets
    \item evaluate student model on original, manually labeled datasets
    \item repeat
\end{enumerate}

@@

\subsection{WER}

\subsection{PER}

@@

\section{Future Work}
\subsection{Adversarial Training}
\subsection{Transform Singing to Speech Data}
remove pitch from singing

\section{Conclusion}

\printbibliography

>>>>

\subsubsection{Jamendo Dataset}
This dataset one of the most popular datasets for AST and has been used by many state-of-the-art
AST models. It contains 20 English songs and 60 songs in other languages with word-aligned timestamped sequences \citep{JamendoLyrics}. This dataset
is a good candidate for training AST models because it is publicly available and it's popularity
makes it an excellent benchmark to compare against other models. However, it is still a relatively
small dataset and does not contain any phoneme sequences. The authors of this dataset were able to
achieve a 77.8\% Word Error Rate (WER) which still leaves a lot of room for improvement.

\subsubsection{Children's Songs Dataset}
This is a dataset of 50 English and 50 Korean children's songs with grapheme level timestamps and
pitches. This dataset was sung by a single professional Korean singer in two separate keys for each
song \citep{ChildrensSongs}. This dataset is a good candidate for training AST models because it
includes the onset and offset information, pitch, and grapheme level timestamps that could be
preprocessed to phoneme or word level timestamps. It is also a very clean dataset because of the
professional performance and setting. The downside of this dataset is that graphemes are
not as popular as phonemes, word or utterance labels in either ASR or AST.

\subsubsection{MUSDB18}
MUSEDB18 is a dataset of 150 songs with isolated vocals and accompaniment tracks \citep{musdb18}. This
dataset is a good candidate for training AST models because it is publicly available and it has
clean isolated vocals. The downside of this dataset is that it doesn't contain any word level
timestamps. However, with the CTC technique mentioned in \ref{sec:utteranceToPhoneme}, this dataset
can still be used to train AST models.

@@

{
\color{red}
Other models focus on the transcription of notes instead of lyrics. These models use a similar
to the ones that are transcribing lyrics
TODO: Add more detail about HMMs
TODO: Write about Dynamic Time Warping
TODO: Write about some results of HMMs
}

@@

For the word alignment task, WhisperX uses an external phoneme alignment approach to generate
word level timestamps using phoneme level timestamps \citep{whisperX}. The external phoneme
alignment model was actually a wav2vec 2.0 model that used Dynamic Time Warping (DTW) \cite{DTW}
to align the phonemes \citep{whisperX}. The first and last phonemes of each word were used to
generate the word level timestamps \citep{whisperX}.

@@

\section{Method}
In order to produce a model that can perform AST, we train a model to first take the audio and align
it with the lyrics like in the last step of the WhisperX pipeline. This helps us create a model that
can poperly annotate phonemes from the audio. Then, a secondary model can be trained to take the
audio and the phoneme annotations to generate the lyrics. With both a lyric and phoneme generator,
any song will be able to be transcribed into lyrics and time-aligned phonemes for an end-to-end AST.

Each step in this process allows for the use of teacher-student techniques mentioned in section
\ref{sec:TeacherStudent} to generate more labeled data from unlabeled data. This is important
because there are so few labeled datasets available for AST.

\subsection{Preprocessing Datasets}
To preprocess datasets, the audio files were preprocessed in the same way WhisperX preprocessed
data with the VAD Cut \& Merge technique \citep{whisperX} except with a slight modification before
trying to detect voices. Since the audio files were songs, most of them will have both singing and
background music. This means that the VAD model will have a harder time detecting when the singing
stops. To help the VAD model, the audio files were first passed through Demucs v4 \citep{Demucs}
to separate the vocals from the background music. Then, the VAD model was used to detect the
voices. Finally, the audio files were cut into segments at the detected voice sections. To reduce
memory requirements and because lyrics utterances are often shorter than 30 seconds, the segments
will be cut into 8-15 second segments. Segments that are shorter than 8 seconds can either be padded
or merged with other segments into segments of 8-15 seconds.

The first subsystem of our AST model will be to take the audio and generate the phoneme annotations.
This subsystem will be trained and tested on the TIMIT, Children's Song and NUS datasets. These are
all datasets that contain phoneme level annotations. TIMIT, although it is a speech dataset, can be
transformed into a pseudo-singing dataset as mentioned in \ref{sec:pseudoSinging} or used directly
as a different variety of vocalizing phonemes.

\subsection{Augmenting Datasets}
There are many ways to augment datasets. The three ways mentioned in SpecAugment includes
time warping, frequency masking and time masking \citep{SpecAugment}. These techniques can be
applied to the audio spectrogram before it is fed into the model. Time warping is a technique that
stretches or compresses the audio spectrogram in the time dimension so it must be handled carefully
to update the labels accodingly. Another way to augment the datasets is to transform the audio
pitch. This can be done by shifting the pitch up or down.

% \subsection{Combining Datasets}

\section{Training}

% \begin{enumerate}
%     \item Preprocess datasets
%     \item Augment datasets
%     \item Create frankenstein dataset
%     \item Train model
%     \item Evaluate model
%     \item Label unlabeled datasets
%     \item train student model on newly labeled datasets
%     \item evaluate student model on original, manually labeled datasets
%     \item repeat
% \end{enumerate}

@@

\subsection{VAD Performance}

\subsection{Phoneme Alignment Performance}
% PER

\subsection{Lyric Generation Performance}
% WER

@@

\section{Future Work}
\subsection{Adversarial Training}
\subsection{Transform Singing to Speech Data}
remove pitch from singing
\subsection{Phoneme to Grapheme}
\citep{G2P} or \citep{P2G}

\section{Conclusion}
\citep{pyannote}
\printbibliography
